Figures

### 2018-07-12 figures/06_k.Rmd
order k figure by connectivity not metric value

# controls ordering of ridge plot
fit_df_iws$key <- factor(fit_df_iws$key, levels = c("k",
                                                    "k1_sr", "k2_sr",
                                                    "k1_bf", "k2_bf",
                                                    "k1_md", "k2_md",
                                                    "k1_lc", "k2_lc",
                                                    "k1_sd", "k2_sd",
                                                    "k1_cd", "k2_cd",
                                                    "k1_ll", "k2_ll", 
                                                    "k1_la", "k2_la"))

k_viz_iws <- ggplot(
  fit_df_iws, 
  aes(x = coef, y = key, fill = key, color = key)) + 
    geom_density_ridges(size = 0.1, scale = 0.7, rel_min_height = 0.01) + 
    geom_hline(yintercept = seq(1.8, 14.8, by = 2)) +
    scale_fill_manual(values = c("grey", 
                            rep(c(viridis::viridis(1, begin = 0.5), 
                                  viridis::viridis(1, begin = 0)), 8))) +
    scale_color_manual(values = c("grey", 
                               rep(c(viridis::viridis(1, begin = 0.5), 
                                     viridis::viridis(1, begin = 0)), 8))) +
    cowplot::theme_cowplot() + theme(panel.grid.major.y = element_blank(),
                                     axis.text = element_text(size = 10),
                                     axis.title = element_text(size = 12),
                               plot.title = element_text(size = 12, face = "bold", hjust = 0),
                                     axis.line.x = element_line(size = 1, 
                                     colour = "black"),
                                     axis.line.y = element_line(size = 1, 
                                                       colour = "black"), 
                                     legend.position = "none", 
                                     plot.margin = margin(0.5,0,0,0, "cm")) + 
  xlab("k Value") + ylab("") + 
  scale_y_discrete(breaks = levels(fit_df_iws$key)[
    c(1, seq(3, length(levels(fit_df_iws$key)), by = 2))], 
                   labels = rev(c("Link length",
                   "Closest lake distance",
                   "Stream density",
                   "Lake connection", 
                   "Upstream lake area",
                   "Max depth",
                   "Baseflow",
                   "Stream order ratio",
                   "Global")))

@@

fit_df_nws$key <- factor(fit_df_nws$key, levels = c("k",
                                                    "k1_sr", "k2_sr",
                                                    "k1_bf", "k2_bf",
                                                    "k1_md", "k2_md",
                                                    "k1_lc", "k2_lc",
                                                    "k1_sd", "k2_sd",
                                                    "k1_cd", "k2_cd",
                                                    "k1_ll", "k2_ll", 
                                                    "k1_la", "k2_la"))

k_viz_nws <- ggplot(
  fit_df_nws, 
  aes(x = coef, y = key, fill = key, color = key)) + 
  geom_density_ridges(size = 0.1, scale = 0.7, rel_min_height = 0.01) + 
  geom_hline(yintercept = seq(1.8, 14.8, by = 2)) +
  scale_fill_manual(values = c("grey",
                               rep(c(viridis::viridis(1, begin = 0.5),
                                     viridis::viridis(1, begin = 0)), 8))) +
  scale_color_manual(values = c("grey", 
                               rep(c(viridis::viridis(1, begin = 0.5), 
                                     viridis::viridis(1, begin = 0)), 8))) +
  cowplot::theme_cowplot() + theme(axis.text = element_text(size = 10),
                                   axis.title = element_text(size = 12),
                               plot.title = element_text(size = 12, face = "bold", hjust = 0),
                                   axis.line.x = element_line(size = 1, 
                                                  colour = "black"),
                                   axis.line.y = element_line(size = 1, 
                                                  colour = "black"), 
                                   legend.position = "none", 
                                   plot.margin = margin(0.5,0,0,-0.7, "cm")) + 
  xlab("k Value") +  ylab("") +
  scale_y_discrete(breaks = levels(fit_df_nws$key)[
    c(1, seq(3, length(levels(fit_df_nws$key)), by = 2))], 
    labels = rev(c("Link length",
                   "Closest lake distance",
                   "Stream density",
                   "Lake connection", 
                   "Upstream lake area",
                   "Max depth",
                   "Baseflow",
                   "Stream order ratio",
                   "Global")))

>>>>

# controls ordering of ridge plot
fit_df_iws$key <- factor(fit_df_iws$key, levels = c("k",
                                                    "k1_sr", "k2_sr",
                                                    "k1_bf", "k2_bf",
                                                    "k2_md", "k1_md",
                                                    "k1_la", "k2_la",
                                                    "k2_lc", "k1_lc",
                                                    "k2_sd", "k1_sd",
                                                    "k1_cd", "k2_cd",
                                                    "k1_ll", "k2_ll"))
# k2  = higher metric value
# right = higher connectivity, purple

k_viz_iws <- ggplot(
  fit_df_iws, 
  aes(x = coef, y = key, fill = key, color = key)) + 
    geom_density_ridges(size = 0.1, scale = 0.7, rel_min_height = 0.01) + 
    geom_hline(yintercept = seq(1.8, 16.8, by = 2)) +
    scale_fill_manual(values = c("grey", 
                            rep(c(viridis::viridis(1, begin = 0.5), 
                                  viridis::viridis(1, begin = 0)), 8))) +
    scale_color_manual(values = c("grey", 
                               rep(c(viridis::viridis(1, begin = 0.5), 
                                     viridis::viridis(1, begin = 0)), 8))) +
    cowplot::theme_cowplot() + theme(panel.grid.major.y = element_blank(),
                                     axis.text = element_text(size = 10),
                                     axis.title = element_text(size = 12),
                               plot.title = element_text(size = 12, face = "bold", hjust = 0),
                                     axis.line.x = element_line(size = 1, 
                                     colour = "black"),
                                     axis.line.y = element_line(size = 1, 
                                                       colour = "black"), 
                                     legend.position = "none", 
                                     plot.margin = margin(0.5,0,0,0, "cm")) + 
  xlab("k Value") + ylab("") + 
  scale_y_discrete(breaks = levels(fit_df_iws$key)[
    c(1, seq(3, length(levels(fit_df_iws$key)), by = 2))], 
                   labels = rev(c("Link length",
                   "Closest lake distance",
                   "Stream density",
                   "Lake connection", 
                   "Upstream lake area",
                   "Max depth",
                   "Baseflow",
                   "Stream order ratio",
                   "Global")))

@@

fit_df_nws$key <- factor(fit_df_nws$key, levels = c("k",
                                                    "k1_sr", "k2_sr",
                                                    "k1_bf", "k2_bf",
                                                    "k2_md", "k1_md",
                                                    "k1_la", "k2_la",
                                                    "k2_lc", "k1_lc",
                                                    "k2_sd", "k1_sd",
                                                    "k1_cd", "k2_cd",
                                                    "k1_ll", "k2_ll"))
# k2  = higher metric value
# right = higher connectivity, purple

k_viz_nws <- ggplot(
  fit_df_nws, 
  aes(x = coef, y = key, fill = key, color = key)) + 
  geom_density_ridges(size = 0.1, scale = 0.7, rel_min_height = 0.01) + 
  geom_hline(yintercept = seq(1.8, 16.8, by = 2)) +
  scale_fill_manual(values = c("grey",
                               rep(c(viridis::viridis(1, begin = 0.5),
                                     viridis::viridis(1, begin = 0)), 8))) +
  scale_color_manual(values = c("grey", 
                               rep(c(viridis::viridis(1, begin = 0.5), 
                                     viridis::viridis(1, begin = 0)), 8))) +
  cowplot::theme_cowplot() + theme(axis.text = element_text(size = 10),
                                   axis.title = element_text(size = 12),
                               plot.title = element_text(size = 12, face = "bold", hjust = 0),
                                   axis.line.x = element_line(size = 1, 
                                                  colour = "black"),
                                   axis.line.y = element_line(size = 1, 
                                                  colour = "black"), 
                                   legend.position = "none", 
                                   plot.margin = margin(0.5,0,0,-0.7, "cm")) + 
  xlab("k Value") +  ylab("") +
  scale_y_discrete(breaks = levels(fit_df_nws$key)[
    c(1, seq(3, length(levels(fit_df_nws$key)), by = 2))], 
    labels = rev(c("Link length",
                   "Closest lake distance",
                   "Stream density",
                   "Lake connection", 
                   "Upstream lake area",
                   "Max depth",
                   "Baseflow",
                   "Stream order ratio",
                   "Global")))
